Assessing landscape N removal in coastal New England catchments using the N-Sink

### 2023-04-27 manuscript/manuscript.Rmd
no longer loading rda

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  cache = FALSE,
  tidy = FALSE,
  message = FALSE
)
#load(system.file("testdata.rda", package = "nsink"))
load("testdata.rda")
```

>>>>

```{r, include = FALSE}
knitr::opts_chunk$set(
  eval = TRUE,
  cache = FALSE,
  tidy = FALSE,
  message = FALSE
)
#load(system.file("testdata.rda", package = "nsink"))
#load("testdata.rda")
```
